Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-03 doc/PRF2022/PRF_main.tex
yny

\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
To begin, we place the bilayer structure (with BC (i)) from the inset of
Figure~\ref{fig:relax}(b) in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate, and ${\ee}_x$ and
${\ee}_y$ are horizontal and vertical unit vectors, respectively. The
initial bilayer structure consists of a small self-enclosing bilayer
(vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c) shows a snapshot at $t = 0.5$
$\upmu$s of the bilayer for different shear rates $\dot\gamma=
0.05,0.075,0.01$. The dynamics of the bilayer can be found in the
supplementary movies, which show that the initial pieces of bilayers
merge and form a worm-like shape under a linear shear flow. At a low
shear rate, the bilayer constantly goes through rotation and extensional
deformation with the whole bilayer remaining intact
(Figure~\ref{fig:BC1_shear}(a)). As the shear rate increases to a
moderate value (Figure~\ref{fig:BC1_shear}(b)), the bilayer is observed
to shed a small piece of bilayer, similar to the asymmetric breakup of a
viscous drop \cite{} \todo[inline]{missing citation}. In
Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
separate, nearly equal bilayers, similar to the symmetric drop breakup
under a linear shear flow \cite{} \todo[inline]{missing citation}.
%%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
% The streamlines are plotted in the background. 
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%  }
%\end{figure}

>>>>

\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
To begin, we place the bilayer structure (with BC (i)) from the inset of
Figure~\ref{fig:relax}(b) in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate, and ${\ee}_x$ and
${\ee}_y$ are horizontal and vertical unit vectors, respectively. The
initial bilayer structure consists of a small self-enclosing bilayer
(vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c) shows a snapshot at $t = 0.5$
$\upmu$s of the bilayer for different shear rates $\dot\gamma=
0.05,0.075,0.01$. The dynamics of the bilayer can be found in the
supplementary movies, which show that the initial pieces of bilayers
merge and form a worm-like shape under a linear shear flow. At a low
shear rate, the bilayer constantly goes through rotation and extensional
deformation with the whole bilayer remaining intact
(Figure~\ref{fig:BC1_shear}(a)). As the shear rate increases to a
moderate value (Figure~\ref{fig:BC1_shear}(b)), the bilayer is observed
to shed a small piece of bilayer, similar to the asymmetric breakup of a
viscous drop in confinement \cite{DuFuZhuMaLi2016_AICHEJ}.
%\todo[inline]{missing citation}. 
In Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
separate, nearly equal bilayers, similar to the symmetric drop breakup
under a linear shear flow \cite{Stone1994_ARFM}. 
%\todo[inline]{missing citation}.
%%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
% The streamlines are plotted in the background. 
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%  }
%\end{figure}
